\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amscd}
\usepackage{amsfonts}
\usepackage{graphicx}%
\usepackage{fancyhdr}


\theoremstyle{plain} \numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{finalremark}[theorem]{Final Remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}{Question} \topmargin-2cm

%\newcommand{\kl}[1]{\marginpar{\sc KL}{\bf #1}}
\newcommand{\kl}[1]{}

\newcommand{\comment}[1]{}
\textwidth6in

\setlength{\topmargin}{0in} \addtolength{\topmargin}{-\headheight}
\addtolength{\topmargin}{-\headsep}

\setlength{\oddsidemargin}{0in}

\oddsidemargin  0.0in \evensidemargin 0.0in \parindent0em

\pagestyle{fancy}\lhead{List of Publications} \rhead{August 2020}
\chead{{\large{\bf Kenny Zhuo Ming Lu}}} \lfoot{} \rfoot{\bf \thepage} \cfoot{}

\newcounter{list}

\begin{document}

\raisebox{1cm}
%\section{Publications}

{\bf Book Chapter}
\begin{enumerate}
\item Lean Launch Data Engineering Projects With Super
    Type Power. \textit{Kenny Zhuo Ming Lu}, Pg 119 - 132. Innovative
    Technologies for Market Leadership: Investing in the
    Future. Editors, \textit{Glauner and Plugmann}, 2020, Springer,
    ISBN 978-3-030-41308-8.
\end{enumerate}



{\bf Journal Publications}
\begin{enumerate}
\item Derivative-Based Diagnosis of Regular Expression
  Ambiguity. \textit{Martin Sulzmann and Kenny Zhuo Ming Lu} IJFCS 2017.
\end{enumerate}


{\bf Conference Publications}
\begin{enumerate}
\item  Solving of Regular Equations Revisited. \textit{Martin Sulzmann
    and Kenny Zhuo Ming Lu}, ICTAC 2019. Hammamet, Tunisia 2019  
\item Control flow obfuscation via CPS transformation. \textit{Kenny
    Zhuo Ming Lu}  PEPM@POPL 2019: 54-60, Cascais, Portugal 2019 
\item Derivative-Based Diagnosis of Regular Expression
  Ambiguity. \textit{Martin Sulzmann and Kenny Zhuo Ming Lu} CIAA 2016.
\item Implementing Cost-effective Data Collection and Extraction
  Processes with CollaMine. \textit{Kenny Zhuo Ming Lu and Belson
    Heng} ICCCRI 2016.
\item POSIX Regular Expression Parsing with Derivatives. \textit{Martin Sulzmann, Kenny Zhuo Ming Lu}  FLOPS 2014  
\item Finding Near Duplicates in Short Text Messages in Singlish Using
  MapReduce and Phonetic Matching. \textit{ Jophia Yi Wen Soh and
    Kenny Zhuo Ming Lu} ICCCRI 2014
\item Regular Expression Sub-Matching using Partial Derivatives. \textit{Martin Sulzmann and Kenny Zhuo Ming Lu} 
In Proceedings of the 14th International Symposium on Principles and Practice of Declarative Programming, PPDP 2012, Leuven, Belgium, September, 2012
\item XHaskell - adding regular expression types to Haskell. \textit{Martin Sulzmann and Kenny Zhuo Ming Lu} 
In Proceedings of the 19th International Symposium on Implementation and Application of Functional Languages, IFL 2007, Freiburg Germany, October 2007.
\item XHaskell - adding regular expression types to Haskell. \textit{Kenny Zhuo Ming Lu} 
In poster session of the Fifth Asian Symposium of Programming Languages and Systems, APLAS 2007,
Singapore. November 29 - December 1 2007.
\item XHaskell - adding regular expression types to Haskell. \textit{Martin Sulzmann and Kenny Zhuo Ming Lu} 
In Proceedings of the 19th International Symposium on Implementation and Application of Functional Languages, IFL 2007, Freiburg Germany, October 2007.
\item XHaskell \textit{Martin Sulzmann and Kenny Zhuo Ming Lu} 
In demo presentation of PLAN-X 2006, Charleston, USA, Jan 2006
\item A Type-Safe Embedding of XDuce into ML. \textit{Martin Sulzmann and Kenny Zhuo Ming Lu} In Proceedings of
the ML Workshop 2005, Tallinn Estonia. Electronic Notes in Computer Science, pages 229-253, 2005 
\item An Implementation of Subtyping among Regular Expression Types. \textit{Kenny Zhuo Ming Lu and Martin Sulzmann} In proceedings of the Second Asian Symposium of Programming Languages and Systems, APLAS 2004, Taipei, Taiwan, November 4-6, 2004. Proceedings. Lecture Notes in Computer Science 3302 Springer 2004.
\end{enumerate}


\end{document}